Microphysics and astrophysics inspired priors for neutron star mergers

### 2025-02-13 paper.tex
fixing typos breaking compilation

\documentclass[twocolumn]{aastex631}
\usepackage{siunitx}
\usepackage{amsmath}

@@

	In this work, we advocate using these physics-inspired priors joint priors on $\mathcal{M}$ and $\tilde{\Lambda}$, which are the two best measured and most informative parameters related to the neutron star equation of state. We show an improvement on the measurement of the marginalized posterior on $\tilde{\Lambda}$ from the gravitational-wave observation of GW170817 from $\tilde{\Lambda}=\red{XX}$ with the agnostic prior to $\red{YY}$ with the new physics-inspired prior. This corresponds to an improvement in the neutron star radius measurement of an equivalent $\unit[1.4]{M_\odot}$ star from $\red{R_{1.4}}= $ to $\red{\ldots}$
	For GW190425, the improvement is \red{\ldots}.

>>>>

\documentclass[twocolumn]{aastex631}
%\usepackage{siunitx}
\usepackage{amsmath}

@@

In this work, we advocate using these physics-inspired priors joint
priors on $\mathcal{M}$ and $\tilde{\Lambda}$, which are the two best
measured and most informative parameters related to the neutron star
equation of state. We show an improvement on the measurement of the
marginalized posterior on $\tilde{\Lambda}$ from the gravitational-wave
observation of GW170817 from $\tilde{\Lambda}=\red{XX}$ with the agnostic
prior to $\red{YY}$ with the new physics-inspired prior. This corresponds
to an improvement in the neutron star radius measurement of an equivalent
$[1.4]\,{M_\odot}$ star from $\red{R_{1.4}}= $ to $\red{\ldots}$ For
GW190425, the improvement is \red{\ldots}.
